Implementation and comparison of register allocation to translate \lstinline!LLVM--! to x86

### 2023-11-29 article.tex
Intro basic blocks before terms

>>>>

These contiguous sequences of instructions are referred to as \textit{basic blocks}: a basic block is defined as a sequence of instructions with no branches in or out except for the first and last instructions, and can be collectively construed of as a node in a control flow graph, whose directed entry edges are from any block that directs control flow towards itself.
